---
title: "Strava club VTT Saint-Germain-en-Laye"
#runtime: shiny
output:
  #html_document
  flexdashboard::flex_dashboard:
    orientation: columns
    #vertical_layout: scroll
    #logo: img.png
    favicon: img.png
---
<style>                     
.navbar-brand {
  background-color: #fc4c02;
}
.avatars {
  margin-bottom: 5px;
}
.avatar-athlete {
  width: 32px;
  height: 32px;
  border-radius: 50%;
}
.avatar-athlete:hover {
  transform: scale(2);
}
.blur {
    opacity: 0.1;
    filter: alpha(opacity=10); /* For IE8 and earlier */
}
table {
  float: left;
}
</style>       

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r libraries, warning = FALSE, message = FALSE}
library(data.table)
library(stringr)
library(flexdashboard)
library(DT)
library(htmltools)
library(rvest)
library(ggplot2)
library(plotly)
library(scales)
library(lubridate)
library(knitr)
```

```{r load data}
#file <- "../../Robject/athl_data_2017-12-26.rds"
file <- rev(list.files("../../Robject", "^athl_data_20", full.names = TRUE))[1]
dt.athl <- readRDS(file)
```

<!---data processing--->

```{r club metadata}
id <- "28259"
url <- paste0("https://www.strava.com/clubs/", id)
avatar <- "https://dgalywyr863hv.cloudfront.net/pictures/clubs/28259/698625/1/large.jpg"
name <- "VTT Saint-Germain-en-Laye"
location <- "Saint-Germain-en-Laye"
```

```{r date values}
view <- str_extract(file, "[0-9\\-]+")
ym <- dt.athl[!is.na(cm), unique(cm)]
m <- str_sub(ym, 5, 7) %>% as.integer()
y <- str_sub(ym, 1, 4) %>% as.integer()
l13m <- paste(c(month.name[m:12], month.name[1:m]), c(rep(y-1, m-11), rep(y, m)))
l13m_ <- paste(str_sub(l13m, 1, 3), str_sub(l13m, -4), sep = ". ")
```

```{r athlete data}
# modify name
dt.athl[, tempo := .N, by = .(word(name))]
dt.athl[, name_ := ifelse(tempo == 1, word(name), paste0(str_extract(name, "[\\w]+ \\w"), "."))]
dt.athl[, name_ := str_to_title(name_)]
dt.athl[, tempo := NULL]
# column order
setcolorder(dt.athl, c(1:3, 31, 4:5, 7, 6, 8, 18:30, 9, 13, 11, 10, 12, 17, 15, 14, 16))
```

```{r data conso}
sdcols <- str_subset(names(dt.athl), "_all_")
dt.sum_all <- dt.athl[, lapply(.SD, sum), .SDcols = sdcols, by = cm]
sdcols <- str_subset(names(dt.athl), "^(ytd_)|(at_)")[-1]
dt.sum_ytd_at <- dt.athl[, lapply(.SD, sum), .SDcols = sdcols, by = .(cm, ytd_at_activity)]
```

```{r add stats}
q.addstats_all <- quote(`:=`(cm_all_speed = cm_all_dist / as.numeric(cm_all_time) * 3600,
                             cm_all_elevspeed = cm_all_elev / as.numeric(cm_all_time) * 3600,
                             cm_all_slope = cm_all_elev / cm_all_dist / 1000,
                             l12m_all_dist = rowSums(.SD)))
q.addstats_ytd_at <- quote(`:=`(ytd_time_mean = ytd_time / ytd_nb,
                                ytd_dist_mean = ytd_dist / ytd_nb,
                                ytd_elev_mean = ytd_elev / ytd_nb,
                                ytd_speed = ytd_dist / as.numeric(ytd_time) * 3600,
                                ytd_elevspeed = ytd_elev / as.numeric(ytd_time) * 3600,
                                ytd_slope = ytd_elev / ytd_dist / 1000,
                                at_time_mean = at_time / at_nb,
                                at_dist_mean = at_dist / at_nb,
                                at_elev_mean = at_elev / at_nb,
                                at_speed = at_dist / as.numeric(at_time) * 3600,
                                at_elevspeed = at_elev / as.numeric(at_time) * 3600,
                                at_slope = at_elev / at_dist / 1000))
sdcols <- str_subset(names(dt.athl), "^m-")[-1]
dt.athl[, eval(q.addstats_all), .SDcols = sdcols]
dt.athl[, eval(q.addstats_ytd_at)]
dt.sum_all[, eval(q.addstats_all), .SDcols = sdcols]
dt.sum_ytd_at[, eval(q.addstats_ytd_at)]
```

```{r replace non finite values by 0}
sdcols <- str_subset(names(dt.athl), "((speed)|(slope)|(mean))$")
dt.athl[, c(sdcols) := lapply(.SD, function(x) ifelse(is.finite(x), x, 0)), .SDcols = sdcols]
```

```{r columns name}
cols <- names(dt.athl)
cols_dist <- str_subset(cols, "_dist(_mean)*$")
cols_time <- str_subset(cols, "_time(_mean)*$")
cols_elev <- str_subset(cols, "_elev(_mean)*$")
cols_speed <- str_subset(cols, "_speed$")
cols_elevspeed <- str_subset(cols, "_elevspeed$")
cols_slope <- str_subset(cols, "_slope$")
cols_nb <- str_subset(cols, "_nb$")
cols_mean <- str_subset(cols, "_mean$")
```

```{r function to format as character}
# time as character and preserve order 
f.duration_to_char <- function(x) {
  period <- round(x) %>% seconds_to_period() %>% str_sub(1, -4)
  d <- str_extract(period, "[0-9]+d") %>% str_pad(4)
  h <- str_extract(period, "[0-9]+H") %>% str_pad(3)
  m <-str_extract(period, "[0-9]+M") %>% str_pad(3)
  dhm <- paste(d, h , m) %>% str_replace_all("NA", "") %>% str_to_lower() %>% str_pad(12)
}
# numeric to character
f.num_to_char <- function(x, nsmall = 0L, suffix = NULL) {
  format(x, nsmall = nsmall, digits = 0, big.mark = " ", scientific = FALSE) %>%
    paste(suffix) %>%
    str_trim()
}
```

```{r club data for value boxes, eval = FALSE}
dt.vb <- copy(dt.sum)
dt.vb[, c(cols_dist) := lapply(.SD, f.num_to_char, suffix = "km"), .SDcols = cols_dist]
dt.vb[, c(cols_time) := lapply(.SD, f.duration_to_char), .SDcols = cols_time]
dt.vb[, c(cols_elev) := lapply(.SD, f.num_to_char, suffix = "m"), .SDcols = cols_elev]
dt.vb[, c(cols_speed) := lapply(.SD, f.num_to_char, nsmall = 1, suffix = "km/h"), .SDcols = cols_speed]
dt.vb[, c(cols_elevspeed) := lapply(.SD, f.num_to_char, suffix = "m/h"), .SDcols = cols_elevspeed]
dt.vb[, c(cols_slope) := lapply(.SD, function(x) sprintf(fmt = "%.1f%%", 100 * x)), .SDcols = cols_slope]
dt.vb[, c(cols_nb) := lapply(.SD, f.num_to_char), .SDcols = cols_nb]
```

```{r colors}
color_dist <- rgb(0, 0, 1)
color_time <- rgb(0, 1, 0)
color_elev <- rgb(1, 0, 0)
color_nb <- rgb(1/3, 1/3, 1/3)
# function to average colors
f.averagecolor <- function(...) {
  mixcolor <- rowMeans(col2rgb(c(...)))
  color <- rgb(mixcolor["red"], mixcolor["green"], mixcolor["blue"], maxColorValue = 255)
}
```

```{r cols info data}
dt.cols_info <- data.table(col = names(dt.athl))
dt.cols_info[col %chin% cols_dist, `:=`(label = "Distance (km)", color = color_dist)]
dt.cols_info[col %chin% cols_time, `:=`(label = "Time", color = color_time)]
dt.cols_info[col %chin% cols_elev, `:=`(label = "Elevation (m)", color = color_elev)]
dt.cols_info[col %chin% cols_speed, `:=`(label = "Speed (km/h)", color = f.averagecolor(color_dist, color_time))]
dt.cols_info[col %chin% cols_elevspeed, `:=`(label = "Elevation speed (m/h)", color = f.averagecolor(color_elev, color_time))]
dt.cols_info[col %chin% cols_slope, `:=`(label = "Slope", color = f.averagecolor(color_elev, color_dist))]
dt.cols_info[col %chin% cols_nb, `:=`(label = "Activities", color = color_nb)]
dt.cols_info[col %chin% cols_mean, label := paste("Average", str_to_lower(label))]
dt.cols_info[col %chin% str_subset(cols_mean,"_dist_"), color := f.averagecolor(color_dist, color_nb)]
dt.cols_info[col %chin% str_subset(cols_mean,"_time_"), color := f.averagecolor(color_time, color_nb)]
dt.cols_info[col %chin% str_subset(cols_mean,"_elev_"), color := f.averagecolor(color_elev, color_nb)]
cols <- c(str_subset(dt.cols_info$col, "^m-"), "l12m_all_dist")
dt.cols_info[col %chin% cols, label := c(l13m, "Last 12 months")]
dt.cols_info[col == "name_", label := "Athlete"]
```

```{r function for value boxes}
f.valueboxes <- function(dt) {
  vbs <- lapply(names(dt), function(i) {
    value <- dt[[i]]
    if (str_detect(i, "_dist(_mean)*$")) value <- f.num_to_char(value, suffix = "km")
    if (str_detect(i, "_time(_mean)*$")) value <- f.duration_to_char(value)
    if (str_detect(i, "_elev(_mean)*$")) value <- f.num_to_char(value, suffix = "m")
    if (str_detect(i, "_speed$")) value <- f.num_to_char(value, nsmall = 1, suffix = "km/h")
    if (str_detect(i, "_elevspeed$")) value <- f.num_to_char(value, suffix = "m/h")
    if (str_detect(i, "_slope$")) value <- sprintf(fmt = "%.1f%%", 100 * value)
    if (str_detect(i, "_nb$")) value <- f.num_to_char(value)
    caption <- dt.cols_info[col == i, label] %>% str_replace_all(" \\(.+\\)$", "")
    #valueBox(value, caption, color = "#fc4c02")
    valueBox(value, caption)
  })
  out <- lapply(seq_along(vbs), function(i) {
    knit_expand(text = sprintf("###\n\n `r vbs[[%d]]` \n", i))
  })
  knit(text = paste(out, collapse = "\n"))
}
```

```{r function for datatable}
f.datatable <- function(dt, col_desc_order = NULL) {
  # add average
  sdcols <- names(dt)[sapply(dt, is.numeric)]
  dt.mean <- dt[, lapply(.SD, mean, na.rm = TRUE), .SDcols = sdcols]
  dt.mean[, name_ := " average"]
  dt <- rbind(dt, dt.mean, fill = TRUE)
  # format name
  dt[, name_ := paste0("<nobr>", name_, "</nobr>")]
  # format time
  sdcols <- str_subset(names(dt), "_time(_mean)*$")
  dt[, c(sdcols) := lapply(.SD, f.duration_to_char), .SDcols = sdcols]
  dt[, c(sdcols) := lapply(.SD, str_replace_all, pattern = " ", replacement = "&nbsp;&nbsp"), .SDcols = sdcols]
  # replace 0 with NA
  sdcols <- names(dt)[sapply(dt, is.numeric)]
  dt[, c(sdcols) := lapply(.SD, function(x) ifelse(x == 0, NA, x)), .SDcols = sdcols]
  # column names
  colnames <- sapply(names(dt), function(x) {
    dt.cols_info[col == x, label]
  })
  l13m <- str_subset(colnames, "[0-9]{4}$")
  l13m_ <- paste0(str_sub(l13m, 1, 3), ifelse(str_count(l13m) > 8, ". ", " "), str_sub(l13m, -4))
  colnames[colnames %chin% l13m] <- l13m_
  names(colnames) <- NULL
  # index time columns
  cols_time_index <- str_which(names(dt.athl_), "_time(_mean)*$")
  # datatable
  datatable <- datatable(dt,
                         class = "cell-border compact",
                         rownames = FALSE,
                         colnames = colnames,
                         escape = FALSE,
                         options = list(pageLength = nrow(dt),
                                        autoWidth = TRUE,
                                        columnDefs = list(list(orderSequence = c("desc", "asc"), targets = "_all"),
                                                          #list(width = "120px", targets = 0),
                                                          list(width = "50px", targets = 1:(length(dt)-1)),
                                                          list(className = 'dt-right', targets = cols_time_index - 1)),
                                        order = list(col_desc_order, 'desc'),
                                        dom = "t")) %>%
    formatRound(str_subset(names(dt), "_dist$"), digits = 0, mark = " ") %>%
    formatRound(str_subset(names(dt), "_dist_mean$"), digits = 1, mark = " ") %>%
    formatRound(str_subset(names(dt), "_elev"), digits = 0, mark = " ") %>%
    formatRound(str_subset(names(dt), "_speed"), digits = 1, mark = " ") %>%
    formatPercentage(str_subset(names(dt), "_slope"), digits = 1, mark = " ") %>%
    formatRound(str_subset(names(dt), "_nb"), digits = 0, mark = " ")
  # background average row
  datatable <- datatable %>%
    formatStyle(columns = 1,
                target = "row",
                backgroundColor = styleEqual(dt[.N, 1], "#65A2E8"),
                color = styleEqual(dt[.N, 1], "white"),
                fontWeight = styleEqual(dt[.N, 1], "bold"))
  # background cells
  for (col in names(dt)[-1]) {
    datatable <- datatable %>%
      formatStyle(col,
                  backgroundColor = styleEqual(sort(dt[[col]][-1],
                                                    decreasing = TRUE)[1:3],
                                               c("#FFD700", "#CECECE", "#965A38")))
  }
  return(datatable)
}
```

```{r function for graphs}
f.ggplot <- function(dt, x, y = NULL) {
  cols_time <- str_subset(names(dt), "_time(_mean)*$")
  if (length(cols_time)) dt[, c(cols_time) := lapply(.SD, as.numeric), .SDcols = cols_time]
  xlabel <- dt.cols_info[col == x, label]
  xcolor <- dt.cols_info[col == x, color]
  labels <- format_format(big.mark = " ", decimal.mark = ".", scientific = FALSE)
  if (str_detect(x, "_slope$")) labels <- percent
  xcbreaks <- cbreaks(c(0, max(dt[[x]])), pretty_breaks(3), labels)
  xbreaks <- xcbreaks$breaks
  xlabels <- xcbreaks$labels
  if (str_detect(x, "_time")) {
    hd <- ifelse(max(dt[[x]]) < 24 * 3600 * 4, 1, 24)
    cbreaks <- cbreaks(c(0, max(dt[[x]])) / 3600 / hd, pretty_breaks(3))
    xbreaks <- cbreaks$breaks * 3600 * hd
    xlabels <- paste0(cbreaks$breaks, ifelse(hd == 1, "h", "d"))
  }
  sdcols <- str_subset(cols, "^m-")
  xmax <- ifelse(str_detect(x, "^m-"), dt[, max(.SD), .SDcols = sdcols], NA)     
  if (is.null(y)) {
    ggplot(dt, aes(reorder(name_, get(x)), get(x))) +
      geom_col(fill = xcolor) +
      coord_flip() +
      scale_y_continuous(breaks = xbreaks, labels = xlabels, position = "top", limits = c(0, xmax)) +
      geom_hline(yintercept = as.numeric(mean(dt[[x]])), color = "#65A2E8") +
      labs(subtitle = xlabel, x = NULL, y = NULL) +
      theme(title = element_text(color = xcolor),
            axis.text.x = element_text(color = xcolor),
            axis.ticks.x = element_line(color = xcolor),
            plot.background = element_rect(color = "black"))
  } else {
    ylabel <- dt.cols_info[col == y, label]
    ycolor <- dt.cols_info[col == y, color]
    color <- f.averagecolor(xcolor, ycolor)
    labels <- format_format(big.mark = " ", decimal.mark = ".", scientific = FALSE)
    if (str_detect(y, "_slope$")) labels <- percent
    ycbreaks <- cbreaks(c(0, max(dt[[y]])), pretty_breaks(3), labels)
    ybreaks <- ycbreaks$breaks
    ylabels <- ycbreaks$labels
    if (str_detect(y, "_time")) {
      hd <- ifelse(max(dt[[y]]) < 24 * 3600 * 4, 1, 24)
      ybreaks <- cbreaks(range(dt[[y]]) / 3600 / hd)$breaks
      ylabels <- paste0(ybreaks, ifelse(hd == 1, "h", "d"))
      ybreaks <- ybreaks * 3600 * hd
    }
    ggplot(dt, aes(get(x), get(y))) +
      geom_vline(xintercept = as.numeric(mean(dt[[x]])), color = "#65A2E8") +
      geom_hline(yintercept = as.numeric(mean(dt[[y]])), color = "#65A2E8") +
      geom_jitter(col = color) +
      scale_x_continuous(breaks = xbreaks, labels = xlabels) +
      scale_y_continuous(breaks = ybreaks, labels = ylabels) +
      labs(x = xlabel, y = ylabel) +
      theme(title = element_text(colour = color),
            axis.title.x = element_text(color = xcolor),
            axis.text.x = element_text(color = xcolor),
            axis.ticks.x = element_line(color = xcolor),
            axis.title.y = element_text(color = ycolor),
            axis.text.y = element_text(color = ycolor),
            axis.ticks.y = element_line(color = ycolor),
            plot.background = element_rect(color = "black"))
  }  
}
```

```{r div with avatars and links}
avatars <- div(class = "avatars",
               a(href = url,
                 img(src = avatar,
                     title = name,
                     width = "64px",
                     height = "64px",
                     class = "avatar-club",
                     alt = "Avatar")),
               lapply(1:nrow(dt.athl), function(x) {
                 a(href = paste0("https://www.strava.com/athletes/", dt.athl$id[x]),
                   img(src = dt.athl$avatar[x],
                       title = dt.athl$name_[x],
                       class = "avatar-athlete",
                       alt = "Avatar"))
               })
)
```



<!---display dashboard--->

```{r}
source <- paste("strava athletes public data as at", view)
```


`r (page <- paste0(last(l13m), " - All activities"))`
===

__`r page`__ (_`r source`_)

```{r}
avatars
```

```{r}
cols <- str_subset(names(dt.athl), "^cm_")
dt.vb <- dt.sum_all[!is.na(cm), mget(cols)]
dt.athl_ <- dt.athl[, mget(c("name_", cols))]
```

Column {data-width=1}
---

`r f.valueboxes(dt.vb)`

Column {.tabset .tabset-fade}
---

### Bar plots
```{r, fig.width = 3.5, fig.height = 3.5}
for (col in cols) plot(f.ggplot(dt.athl_, col))
```

### Athletes table
`r f.datatable(dt.athl_, 1)`

### Scatterplots
```{r, fig.width = 3.5, fig.height = 3.5}
prefix <- unique(str_extract(cols, "^([a-z]+_){2}"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "dist"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "dist"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "elevspeed"))
```



`r (page <- "Last months distance - All activities")`
===

__`r page`__ (_`r source`_)

```{r}
avatars
```

```{r}
cols <- c(str_subset(names(dt.athl), "^m-"), "l12m_all_dist") %>% rev()
dt.vb <- dt.sum_all[!is.na(cm), mget(cols)]
dt.athl_ <- dt.athl[, mget(c("name_", cols))]
```

Column {data-width=1}
---

`r f.valueboxes(dt.vb)`

Column {.tabset .tabset-fade}
---

### Bar plots
```{r, fig.width = 10.5, fig.height = 3.5}
f.ggplot(dt.athl_, cols[1])
```
```{r, fig.width = 3.5, fig.height = 3.5}
for (col in cols[-1]) plot(f.ggplot(dt.athl_, col))
```

### Athletes table
`r f.datatable(dt.athl_, 1)`

```{r, eval = FALSE}
prefix <- unique(str_extract(cols, "^([a-z]+_){2}"))
```



`r (page <- paste0(y, " year to date - Bike activities"))`
===

__`r page`__ (_`r source`_)

```{r}
blur <- which(dt.athl$ytd_at_activity != "Cycling")
for (i in blur) {
  class <- avatars$children[[2]][[i]]$children[[1]]$attribs$class
  avatars$children[[2]][[i]]$children[[1]]$attribs$class <- paste(class, "blur")
}
avatars
```

```{r}
cols <- str_subset(names(dt.athl), "^ytd_")[-1]
dt.vb <- dt.sum_ytd_at[!is.na(cm) & ytd_at_activity == "Cycling", mget(cols)]
dt.athl_ <- dt.athl[ytd_at_activity == "Cycling", mget(c("name_", cols))]
```

Column {data-width=1}
---

`r f.valueboxes(dt.vb)`

Column {.tabset .tabset-fade}
---

### Bar plots
```{r, fig.width = 2.8, fig.height = 3.5}
for (col in cols) plot(f.ggplot(dt.athl_, col))
```

### Athletes table
`r f.datatable(dt.athl_, 2)`

### Scatterplots
```{r, fig.width = 3.5, fig.height = 3.5}
prefix <- unique(str_extract(cols, "^([a-z]+_)"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "time"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "dist"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "dist"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "dist"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "elevspeed"))
```



`r (page <- "All time - Bike activities")`
===

__`r page`__ (_`r source`_)

```{r}
avatars
```

```{r}
cols <- str_subset(names(dt.athl), "^at_")
dt.vb <- dt.sum_ytd_at[!is.na(cm) & ytd_at_activity == "Cycling", mget(cols)]
dt.athl_ <- dt.athl[ytd_at_activity == "Cycling", mget(c("name_", cols))]
```

Column {data-width=1}
---

`r f.valueboxes(dt.vb)`

Column {.tabset .tabset-fade}
---

### Bar plots
```{r, fig.width = 2.8, fig.height = 3.5}
for (col in cols) plot(f.ggplot(dt.athl_, col))
```

### Athletes table
`r f.datatable(dt.athl_, 2)`

### Scatterplots
```{r, fig.width = 3.5, fig.height = 3.5}
prefix <- unique(str_extract(cols, "^([a-z]+_)"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "time"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "dist"))
f.ggplot(dt.athl_, paste0(prefix, "nb"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "dist"))
f.ggplot(dt.athl_, paste0(prefix, "time"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "dist"), paste0(prefix, "elev"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "time_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "dist_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "elevspeed"))
f.ggplot(dt.athl_, paste0(prefix, "elev_mean"), paste0(prefix, "slope"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "speed"))
f.ggplot(dt.athl_, paste0(prefix, "slope"), paste0(prefix, "elevspeed"))
```


